---
title: "Merging_datasets"
author: "Laura Schirlo"
date: "2024-03-28"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

# Dummy example

## Merging labratory data to the existing NHANES2005_2006 dataset from the dietaryindex package

### Loading the dataset from 2005/2006 into R from the dietaryindex package

```{r}
library(dietaryindex)
library(emmeans)
library(devtools)
library(dplyr)
library(haven)
library(readr)
library(foreign)
load("~/Documents/Laura/UNI/Master/Master thesis/R_Scripts/MSC_LAURA/NHANES_combined_GitHub/NHANES_20052006.rda")

```

### Loading the laboratory dataset from 2005/2006 into R from the NHANES website

```{r}
TRYGL <- read.xport("~/Documents/Laura/UNI/Master/Master thesis/R_Scripts/MSC_LAURA/2005_2006/TRYGL_LDL_APO.XPT")
CHOL <- read.xport("~/Documents/Laura/UNI/Master/Master thesis/R_Scripts/MSC_LAURA/2005_2006/TOT_CHOLESTEROL.XPT")
Food_code <- read.xport("~/Documents/Laura/UNI/Master/Master thesis/R_Scripts/MSC_LAURA/2005_2006/Food_Code.XPT")
Modification_code <- read.xport("~/Documents/Laura/UNI/Master/Master thesis/R_Scripts/MSC_LAURA/2005_2006/Modification_Code.XPT")
```

### Merging the two datasets and renaming them

```{r}
merged_list <- c(NHANES_20052006, list(TRYGL))
names(merged_list)[length(merged_list)] <- "LAB_Trygli"
merged_list <- c(merged_list, list(CHOL))
names(merged_list)[length(merged_list)] <- "LAB_Cholesterol"
```

### Adding the labels to the Laboratory data

```{r}

str(merged_list$LAB_Trygli)

attr(merged_list$LAB_Trygli$SEQN, "label") <- "Respondent Sequence number" 
attr(merged_list$LAB_Trygli$WTSAF2YR, "label") <- "Fasting Subsample 2 year MEC Weight" 
attr(merged_list$LAB_Trygli$LBXTR, "label") <- "Triglyceride mg/dL" 
attr(merged_list$LAB_Trygli$LBDTRSI, "label") <- "Triglyceride nmol/L" 
attr(merged_list$LAB_Trygli$LBDLDL, "label") <- "LDL-Cholesterol mg/dL" 
attr(merged_list$LAB_Trygli$LBDLDLSI, "label") <- "LDL-Cholesterol nmol/L" 
attr(merged_list$LAB_Trygli$LBXAPB, "label") <- "Apolipoprotein mg/dL" 
attr(merged_list$LAB_Trygli$LBDAPBSI, "label") <- "Apolipoprotein g/L" 

str(merged_list$LAB_Cholesterol)
attr(merged_list$LAB_Cholesterol$SEQN, "label") <- "Respondent Sequence number" 
attr(merged_list$LAB_Cholesterol$LBXTC, "label") <- "Total Cholesterol (mg/dL)" 
attr(merged_list$LAB_Cholesterol$LBDTCSI, "label") <- "Total Cholesterol (mmol/L)" 
```

## Getting to know the data

### What are the labels?

```{r}
str(merged_list$FPED)
str(merged_list$NUTRIENT)

str(merged_list$NUTRIENT_IND)
str(merged_list$FPED_IND)


```

**Nutrient**:

-   ***For each participant***, daily total energy and nutrient intakes from foods and beverages and whether the amount of food consumed was usual, much more than usual, or much less than usual are included in the ***Total Nutrient Intakes files***

-   a lot of data about fish consumption, information about total kcals as well as protein / carbohydrates / total sugars / dietary fiber / total fat / different fats / Cholesterol /...

**FPED**: = Food Patterns Equivalents Database

-   How much was eaten by one participant on one day, equivalents are often in cups or oz and some in grams and tbsps!

-   number of foods reported

\--\> convert the different equivalents into grams to score the PHDI

+---------------+----------------------------------------+
| 1 oz          | 28.349523125 g                         |
|               |                                        |
| 1 CUP         | dependent on the consistency / density |
|               |                                        |
| 1 tbsp        | dependent on the consistency / density |
+---------------+----------------------------------------+

**FPED_IND** = for every individual participant, there is an entry for every food component they have eaten that day

-   there are many entries per individual for every food component they have consumed

-   the description of what that type of food is analyzed, can be seen here: merged_list\$FPED_IND\$DESCRIPTION or in the Food_Code dataset

### Descriptive analyses

```{r}
summary(merged_list$DEMO$RIDAGEYR, na.rm = T)
#the mean age in the cohort is 27.9, the median is 19 --> rather young
# --> some of them are 0 years old... exclusion?
summary(merged_list$NUTRIENT$DR1TKCAL, na.rm = T)
#mean kcal they consumed is 2027.3
sum(merged_list$NUTRIENT$DR1TKCAL >= 10000, na.rm = T)
sum(merged_list$NUTRIENT$DR1TKCAL <= 100, na.rm = T)
# -->some ate more than 10000kcal and some less than 100, exlcusion?


num_males <- sum(merged_list$DEMO$RIAGENDR == 1, na.rm = TRUE)
num_females <- sum(merged_list$DEMO$RIAGENDR == 2, na.rm = TRUE)
total_individuals <- num_males + num_females
total_individuals
#total individuals are 10'348

(num_males / total_individuals) * 100
percentage_females <- (num_females / total_individuals) * 100
#the percentages are very equal: f = 50.90 / m = 49.09

sum(merged_list$DEMO$RIDRETH1 == 1) #2847 of the people are Mexican-American
sum(merged_list$DEMO$RIDRETH1 == 2) #349 are other Hispanics
sum(merged_list$DEMO$RIDRETH1 == 3) #3928 are Non-Hispanic white
sum(merged_list$DEMO$RIDRETH1 == 4) #2710 are Non-Hispanic black
sum(merged_list$DEMO$RIDRETH1 == 5) #514 are Other race - including multi-race
#not evenly distributed, therefore we use the weights!


sum(merged_list$DEMO$RIDEXPRG ==1, na.rm = T) #382 are pregenant (lab or self-reported)
sum(is.na(merged_list$DEMO$RIDEXPRG)) #there are 6975 missing values !!!


hist(merged_list$NUTRIENT$DR1TKCAL) #pretty skewed, but the outcome is PHDI
```

## Changing some variables to grams

### [Ounces](https://www.nist.gov/pml/owm/approximate-conversions-us-customary-measures-metric) in grams

```{r}
str(merged_list$FPED)
#there are some variables in ounces --> can be converted into gram by mulitplying with 28.35
# https://www.nist.gov/pml/owm/approximate-conversions-us-customary-measures-metric

#function to convert the ounces in grams

ounces_to_gram_conversion <- function(ounces){
  grams <- ounces * 28.35
  return(grams)
}

#DR1T_G_WHOLE_GRAM
merged_list$FPED <- merged_list$FPED %>%
  mutate(DR1T_G_WHOLE_GRAM = ounces_to_gram_conversion(DR1T_G_WHOLE))
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_G_WHOLE_GRAM, .after = DR1T_G_WHOLE)
attr(merged_list$FPED$DR1T_G_WHOLE_GRAM, "label") <- "Whole grains (grams)"  

#DR1T_G_REFINED
merged_list$FPED <- merged_list$FPED %>%
  mutate(DR1T_G_REFINED_GRAM = ounces_to_gram_conversion(DR1T_G_REFINED))
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_G_REFINED_GRAM, .after = DR1T_G_REFINED)
attr(merged_list$FPED$DR1T_G_REFINED_GRAM, "label") <- "Refined or non-whole grains (grams)"

#DR1T_G_TOTAL
merged_list$FPED <- merged_list$FPED %>%
  mutate(DR1T_G_TOTAL_GRAM = ounces_to_gram_conversion(DR1T_G_TOTAL))
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_G_TOTAL_GRAM, .after = DR1T_G_TOTAL)
attr(merged_list$FPED$DR1T_G_TOTAL_GRAM, "label") <- "Total whole and refined grains (grams)"  


#DR1T_PF_MEAT
merged_list$FPED <- merged_list$FPED %>%
  mutate(DR1T_PF_MEAT_GRAM = ounces_to_gram_conversion(DR1T_PF_MEAT))
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_PF_MEAT_GRAM, .after = DR1T_PF_MEAT)
attr(merged_list$FPED$DR1T_PF_MEAT_GRAM, "label") <- "Beef, veal, pork, lamb, game meat; excludes organ meats and cured meat (grams)" 

#DR1T_PF_CUREDMEAT 
merged_list$FPED <- merged_list$FPED %>%
  mutate(DR1T_PF_CUREDMEAT_GRAM  = ounces_to_gram_conversion(DR1T_PF_CUREDMEAT ))
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_PF_CUREDMEAT_GRAM, .after = DR1T_PF_CUREDMEAT )
attr(merged_list$FPED$DR1T_PF_CUREDMEAT_GRAM, "label") <- "Cured/luncheon meat made from beef, pork, or poultry (grams)" 

#DR1T_PF_ORGAN 
merged_list$FPED <- merged_list$FPED %>%
  mutate(DR1T_PF_ORGAN_GRAM  = ounces_to_gram_conversion(DR1T_PF_ORGAN))
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_PF_ORGAN_GRAM, .after = DR1T_PF_ORGAN  )
attr(merged_list$FPED$DR1T_PF_ORGAN_GRAM, "label") <- "Organ meat from beef, veal, pork, lamb, game, and poultry (grams)" 

#DR1T_PF_POULT 
merged_list$FPED <- merged_list$FPED %>%
  mutate(DR1T_PF_POULT_GRAM  = ounces_to_gram_conversion(DR1T_PF_POULT))
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_PF_POULT_GRAM, .after = DR1T_PF_POULT)
attr(merged_list$FPED$DR1T_PF_POULT_GRAM, "label") <- "Chicken, turkey, Cornish hens, and game birds; excludes organ meats and cured meat (grams)" 

#DR1T_PF_SEAFD_HI
merged_list$FPED <- merged_list$FPED %>%
  mutate(DR1T_PF_SEAFD_HI_GRAM  = ounces_to_gram_conversion(DR1T_PF_SEAFD_HI))
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_PF_SEAFD_HI_GRAM, .after = DR1T_PF_SEAFD_HI)
attr(merged_list$FPED$DR1T_PF_SEAFD_HI_GRAM, "label") <- "Seafood (finfish, shellfish and other seafood) high in n-3 fatty acids (grams)" 

#DR1T_PF_SEAFD_LOW
merged_list$FPED <- merged_list$FPED %>%
  mutate(DR1T_PF_SEAFD_LOW_GRAM  = ounces_to_gram_conversion(DR1T_PF_SEAFD_LOW))
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_PF_SEAFD_LOW_GRAM, .after = DR1T_PF_SEAFD_LOW)
attr(merged_list$FPED$DR1T_PF_SEAFD_LOW_GRAM, "label") <- "Seafood (finfish, shellfish and other seafood) low in n-3 fatty acids (grams)" 

#DR1T_PF_MPS_TOTAL
merged_list$FPED <- merged_list$FPED %>%
  mutate(DR1T_PF_MPS_TOTAL_GRAM  = ounces_to_gram_conversion(DR1T_PF_MPS_TOTAL))
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_PF_MPS_TOTAL_GRAM, .after = DR1T_PF_MPS_TOTAL)
attr(merged_list$FPED$DR1T_PF_MPS_TOTAL_GRAM, "label") <- "Total meat, poultry, seafood, organ meats, and cured meat (grams)" 

#DR1T_PF_EGGS
merged_list$FPED <- merged_list$FPED %>%
  mutate(DR1T_PF_EGGS_GRAM  = ounces_to_gram_conversion(DR1T_PF_EGGS))
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_PF_EGGS_GRAM, .after = DR1T_PF_EGGS)
attr(merged_list$FPED$DR1T_PF_EGGS_GRAM, "label") <- "Eggs (chicken, duck, goose, quail) and egg substitutes (grams)" 


#DR1T_PF_SOY
merged_list$FPED <- merged_list$FPED %>%
  mutate(DR1T_PF_SOY_GRAM  = ounces_to_gram_conversion(DR1T_PF_SOY))
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_PF_SOY_GRAM, .after = DR1T_PF_SOY)
attr(merged_list$FPED$DR1T_PF_SOY_GRAM, "label") <- "Soy products, excluding calcium fortified soy milk and immature soybeans (grams)" 

#DR1T_PF_NUTSDS
merged_list$FPED <- merged_list$FPED %>%
  mutate(DR1T_PF_NUTSDS_GRAM  = ounces_to_gram_conversion(DR1T_PF_NUTSDS))
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_PF_NUTSDS_GRAM, .after = DR1T_PF_NUTSDS)
attr(merged_list$FPED$DR1T_PF_NUTSDS_GRAM, "label") <- "Peanuts, tree nuts, and seeds, excludes coconut (grams)" 

#DR1T_PF_LEGUMES 
merged_list$FPED <- merged_list$FPED %>%
  mutate(DR1T_PF_LEGUMES_GRAM  = ounces_to_gram_conversion(DR1T_PF_LEGUMES))
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_PF_LEGUMES_GRAM, .after = DR1T_PF_LEGUMES)
attr(merged_list$FPED$DR1T_PF_LEGUMES_GRAM, "label") <- "Legumes computed as protein foods (grams)" 

#DR1T_PF_TOTAL 
merged_list$FPED <- merged_list$FPED %>%
  mutate(DR1T_PF_TOTAL_GRAM   = ounces_to_gram_conversion(DR1T_PF_TOTAL ))
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_PF_TOTAL_GRAM , .after = DR1T_PF_TOTAL )
attr(merged_list$FPED$DR1T_PF_TOTAL_GRAM , "label") <- "Total meat, poultry, seafood, organ meats, cured meat, eggs, soy, and nuts and seeds; excludes legumes (grams)" 


str(merged_list$FPED)

#DR1T_F_CITMLB/Intact fruits (whole or cut) of citrus, melons, and berries (cup eq.) 
#--> should be in grams and not cup equivalents --> how was the conversion done in other papers?

#- round them up or down or take whole number --> whole number
# - take frozen and raw? --> make three different categories, a very conservative one, a middler one a very open one
# - for total: sum all of them up or take mean of the means? --> sum them all up


```

### Cups into grams

To convert the cups into grams for several variables, an excel list was created. In there, the different foods / drinks were added up in the respective variable, and the mean was taken to get an estimation of the conversion factor. The lists provided on this [website](https://www.ars.usda.gov/northeast-area/beltsville-md-bhnrc/beltsville-human-nutrition-research-center/food-surveys-research-group/docs/fped-methodology/), show which foods / drinks were scored in what variable.

```{r}

#DR1T_F_CITMLB  = intact fruits of citurs melons and berries
DR1T_F_CITMLB_CONVERTER <- 163.38
merged_list$FPED$DR1T_F_CITMLB_GRAM <- NULL
merged_list$FPED$DR1T_F_CITMLB_GRAM <- merged_list$FPED$DR1T_F_CITMLB * DR1T_F_CITMLB_CONVERTER
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_F_CITMLB_GRAM , .after = DR1T_F_CITMLB)
attr(merged_list$FPED$DR1T_F_CITMLB_GRAM , "label") <- "Intact fruits (whole or cut) of citrus, melons, and berries (grams)" 


#DR1T_F_OTHER  = intact fruits, excluding of citurs melons and berries
DR1T_F_OTHER_CONVERTER <- 149.66
merged_list$FPED$DR1T_F_OTHER_GRAM <- NULL
merged_list$FPED$DR1T_F_OTHER_GRAM <- merged_list$FPED$DR1T_F_OTHER * DR1T_F_OTHER_CONVERTER
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_F_OTHER_GRAM , .after = DR1T_F_OTHER)
attr(merged_list$FPED$DR1T_F_OTHER_GRAM , "label") <- "Intact fruits (whole or cut); excluding citrus, melons, and berries  (grams)" 


#DR1T_F_JUICE  = Fuit jucies, citrus and non citrus
DR1T_F_JUICE_CONVERTER <- 250
merged_list$FPED$DR1T_F_JUICE_GRAM <- NULL
merged_list$FPED$DR1T_F_JUICE_GRAM <- merged_list$FPED$DR1T_F_JUICE * DR1T_F_JUICE_CONVERTER
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_F_JUICE_GRAM , .after = DR1T_F_JUICE)
attr(merged_list$FPED$DR1T_F_JUICE_GRAM , "label") <- "Fruit juices, citrus and non citrus (grams)" 

#DR1T_F_TOTAL  = Total intact or cut fruits and fruit juices
DR1T_F_TOTAL_CONVERTER <- 159.92
merged_list$FPED$DR1T_F_TOTAL_GRAM <- NULL
merged_list$FPED$DR1T_F_TOTAL_GRAM  <- merged_list$FPED$DR1T_F_TOTAL * DR1T_F_TOTAL_CONVERTER
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_F_TOTAL_GRAM  , .after = DR1T_F_TOTAL)
attr(merged_list$FPED$DR1T_F_TOTAL_GRAM  , "label") <- "Total intact or cut fruits and fruit juices (grams)" 


#DR1T_F_TOTAL  = Total intact or cut fruits and fruit juices
DR1T_F_TOTAL_CONVERTER <- 159.92
merged_list$FPED$DR1T_F_TOTAL_GRAM <- NULL
merged_list$FPED$DR1T_F_TOTAL_GRAM  <- merged_list$FPED$DR1T_F_TOTAL * DR1T_F_TOTAL_CONVERTER
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_F_TOTAL_GRAM  , .after = DR1T_F_TOTAL)
attr(merged_list$FPED$DR1T_F_TOTAL_GRAM  , "label") <- "Total intact or cut fruits and fruit juices (grams)" 


#DR1T_V_DRKGR = dark green vegetables
DR1T_V_DRKGR_CONVERTER <- 113.02
merged_list$FPED$DR1T_V_DRKGR_GRAM <- NULL
merged_list$FPED$DR1T_V_DRKGR_GRAM  <- merged_list$FPED$DR1T_V_DRKGR * DR1T_V_DRKGR_CONVERTER
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_V_DRKGR_GRAM  , .after = DR1T_V_DRKGR)
attr(merged_list$FPED$DR1T_V_DRKGR_GRAM  , "label") <- "Dark green vegetables (grams)" 


#DR1T_V_REDOR_TOMATO = Tomatoes and tomato products
DR1T_V_REDOR_TOMATO_CONVERTER <- 176.25
merged_list$FPED$DR1T_V_REDOR_TOMATO_GRAM <- NULL
merged_list$FPED$DR1T_V_REDOR_TOMATO_GRAM  <- merged_list$FPED$DR1T_V_REDOR_TOMATO * DR1T_V_REDOR_TOMATO_CONVERTER
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_V_REDOR_TOMATO_GRAM  , .after = DR1T_V_REDOR_TOMATO)
attr(merged_list$FPED$DR1T_V_REDOR_TOMATO_GRAM  , "label") <- "Tomatoes and tomato products (grams)" 




#DR1T_V_REDOR_OTHER = Other red and orange vegetables, excluding tomatoes and tomato products
DR1T_V_REDOR_OTHER_CONVERTER <- 173.44
merged_list$FPED$DR1T_V_REDOR_OTHER_GRAM <- NULL
merged_list$FPED$DR1T_V_REDOR_OTHER_GRAM  <- merged_list$FPED$DR1T_V_REDOR_OTHER * DR1T_V_REDOR_OTHER_CONVERTER
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_V_REDOR_OTHER_GRAM  , .after = DR1T_V_REDOR_OTHER)
attr(merged_list$FPED$DR1T_V_REDOR_OTHER_GRAM  , "label") <- "Other red and orange vegetables, excluding tomatoes and tomato products (grams)" 
str(merged_list$FPED)


#DR1T_V_REDOR_TOTAL = "Total red and orange vegetables (tomatoes + other red and orange)
DR1T_V_REDOR_TOTAL_CONVERTER <- 174.38
merged_list$FPED$DR1T_V_REDOR_TOTAL_GRAM <- NULL
merged_list$FPED$DR1T_V_REDOR_TOTAL_GRAM  <- merged_list$FPED$DR1T_V_REDOR_TOTAL * DR1T_V_REDOR_TOTAL_CONVERTER
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_V_REDOR_TOTAL_GRAM  , .after = DR1T_V_REDOR_TOTAL)
attr(merged_list$FPED$DR1T_V_REDOR_TOTAL_GRAM  , "label") <- "Total red and orange vegetables (tomatoes + other red and orange) (grams)" 
str(merged_list$FPED)


#DR1T_V_STARCHY_POTATO  = White potatoes
DR1T_V_STARCHY_POTATO_CONVERTER <- 147.5
merged_list$FPED$DR1T_V_STARCHY_POTATO_GRAM <- NULL
merged_list$FPED$DR1T_V_STARCHY_POTATO_GRAM  <- merged_list$FPED$DR1T_V_STARCHY_POTATO * DR1T_V_STARCHY_POTATO_CONVERTER
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_V_STARCHY_POTATO_GRAM  , .after = DR1T_V_STARCHY_POTATO)
attr(merged_list$FPED$DR1T_V_STARCHY_POTATO_GRAM  , "label") <- "White potatoes (grams)" 
str(merged_list$FPED)


#DR1T_V_STARCHY_OTHER = Other starchy vegetables, excluding white potatoes
DR1T_V_STARCHY_OTHER_CONVERTER <- 154.13
merged_list$FPED$DR1T_V_STARCHY_OTHER_GRAM <- NULL
merged_list$FPED$DR1T_V_STARCHY_OTHER_GRAM  <- merged_list$FPED$DR1T_V_STARCHY_OTHER * DR1T_V_STARCHY_OTHER_CONVERTER
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_V_STARCHY_OTHER_GRAM  , .after = DR1T_V_STARCHY_OTHER)
attr(merged_list$FPED$DR1T_V_STARCHY_OTHER_GRAM  , "label") <- "Other starchy vegetables, excluding white potatoes (grams)" 
str(merged_list$FPED)

#DR1T_V_STARCHY_TOTAL = Total starchy vegetables (white potatoes + other starchy)
DR1T_V_STARCHY_TOTAL_CONVERTER <- 153.6
merged_list$FPED$DR1T_V_STARCHY_TOTAL_GRAM <- NULL
merged_list$FPED$DR1T_V_STARCHY_TOTAL_GRAM  <- merged_list$FPED$DR1T_V_STARCHY_TOTAL * DR1T_V_STARCHY_TOTAL_CONVERTER
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_V_STARCHY_TOTAL_GRAM  , .after = DR1T_V_STARCHY_TOTAL)
attr(merged_list$FPED$DR1T_V_STARCHY_TOTAL_GRAM  , "label") <- "Total starchy vegetables (white potatoes + other starchy) (grams)" 
str(merged_list$FPED)

#DR1T_V_OTHER = Other vegetables not in the vegetable components listed above
DR1T_V_OTHER_CONVERTER <- 131.88
merged_list$FPED$DR1T_V_OTHER_GRAM <- NULL
merged_list$FPED$DR1T_V_OTHER_GRAM  <- merged_list$FPED$DR1T_V_OTHER * DR1T_V_OTHER_CONVERTER
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_V_OTHER_GRAM  , .after = DR1T_V_OTHER)
attr(merged_list$FPED$DR1T_V_OTHER_GRAM  , "label") <- "Other vegetables not in the vegetable components listed above (grams)" 
str(merged_list$FPED)


#DR1T_V_TOTAL = Total dark green, red and orange, starchy, and other vegetables; excludes legumes
DR1T_V_TOTAL_CONVERTER <- 134.72
merged_list$FPED$DR1T_V_TOTAL_GRAM <- NULL
merged_list$FPED$DR1T_V_TOTAL_GRAM  <- merged_list$FPED$DR1T_V_TOTAL * DR1T_V_TOTAL_CONVERTER
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_V_TOTAL_GRAM  , .after = DR1T_V_TOTAL)
attr(merged_list$FPED$DR1T_V_TOTAL_GRAM  , "label") <- "Total dark green, red and orange, starchy, and other vegetables; excludes legumes (grams)" 
str(merged_list$FPED)


#DR1T_V_LEGUMES = Legumes computed as vegetables
DR1T_V_LEGUMES_CONVERTER <- 175.95
merged_list$FPED$DR1T_V_LEGUMES_GRAM <- NULL
merged_list$FPED$DR1T_V_LEGUMES_GRAM  <- merged_list$FPED$DR1T_V_LEGUMES * DR1T_V_LEGUMES_CONVERTER
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_V_LEGUMES_GRAM  , .after = DR1T_V_LEGUMES)
attr(merged_list$FPED$DR1T_V_LEGUMES_GRAM  , "label") <- "Legumes computed as vegetables (grams)" 
str(merged_list$FPED)


#DR1T_D_MILK = Fluid milk and calcium fortified soy milk
DR1T_D_MILK_CONVERTER <- 227.86
merged_list$FPED$DR1T_D_MILK_GRAM <- NULL
merged_list$FPED$DR1T_D_MILK_GRAM  <- merged_list$FPED$DR1T_D_MILK * DR1T_D_MILK_CONVERTER
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_D_MILK_GRAM  , .after = DR1T_D_MILK)
attr(merged_list$FPED$DR1T_D_MILK_GRAM  , "label") <- "Fluid milk and calcium fortified soy milk (grams)" 
str(merged_list$FPED)


#DR1T_D_YOGURT =Yogurt 
DR1T_D_YOGURT_CONVERTER <- 245
merged_list$FPED$DR1T_D_YOGURT_GRAM <- NULL
merged_list$FPED$DR1T_D_YOGURT_GRAM  <- merged_list$FPED$DR1T_D_YOGURT * DR1T_D_YOGURT_CONVERTER
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_D_YOGURT_GRAM  , .after = DR1T_D_YOGURT)
attr(merged_list$FPED$DR1T_D_YOGURT_GRAM  , "label") <- "Yogurt (grams)" 
str(merged_list$FPED)

#DR1T_D_CHEESE= Cheese
DR1T_D_CHEESE_CONVERTER <- 59.12
merged_list$FPED$DR1T_D_CHEESE_GRAM <- NULL
merged_list$FPED$DR1T_D_CHEESE_GRAM  <- merged_list$FPED$DR1T_D_CHEESE * DR1T_D_CHEESE_CONVERTER
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_D_CHEESE_GRAM  , .after = DR1T_D_CHEESE)
attr(merged_list$FPED$DR1T_D_CHEESE_GRAM  , "label") <- "Cheese (grams)" 
str(merged_list$FPED)



#DR1T_D_TOTAL  = Total milk, yogurt, cheese, and whey
DR1T_D_TOTAL_CONVERTER <- 79.22
merged_list$FPED$DR1T_D_TOTAL_GRAM <- NULL
merged_list$FPED$DR1T_D_TOTAL_GRAM  <- merged_list$FPED$DR1T_D_TOTAL * DR1T_D_TOTAL_CONVERTER
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_D_TOTAL_GRAM  , .after = DR1T_D_TOTAL)
attr(merged_list$FPED$DR1T_D_TOTAL_GRAM  , "label") <- "Total milk, yogurt, cheese, and whey (grams)" 
str(merged_list$FPED)


#DR1T_ADD_SUGARS = Foods defined as added sugars
DR1T_ADD_SUGARS_CONVERTER <- 6.08
merged_list$FPED$DR1T_ADD_SUGARS_GRAM <- NULL
merged_list$FPED$DR1T_ADD_SUGARS_GRAM  <- merged_list$FPED$DR1T_ADD_SUGARS * DR1T_ADD_SUGARS_CONVERTER
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_ADD_SUGARS_GRAM  , .after = DR1T_ADD_SUGARS)
attr(merged_list$FPED$DR1T_ADD_SUGARS_GRAM  , "label") <- "Foods defined as added sugars (grams)" 
str(merged_list$FPED)
```

### Code a new variable that summarizes the variable for non starchy veggies

```{r}
merged_list$FPED <- merged_list$FPED %>%
  mutate(DR1T_Total_Non_starchy_Veggies = DR1T_V_DRKGR_GRAM +  DR1T_V_REDOR_TOTAL_GRAM+ DR1T_V_OTHER_GRAM)
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_Total_Non_starchy_Veggies  , .after = DR1T_V_TOTAL_GRAM)
attr(merged_list$FPED$DR1T_Total_Non_starchy_Veggies  , "label") <- "Total non starchy veggies consumed (grams)" 


```

### Code a new variable that includes the seafood and substitutes variables low and high in N-3 fatty acids

```{r}
merged_list$FPED <- merged_list$FPED %>%
  mutate(DR1T_Total_Seafood_Sub = DR1T_PF_SEAFD_HI_GRAM +  DR1T_PF_SEAFD_LOW_GRAM)
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_Total_Seafood_Sub , .after = DR1T_PF_SEAFD_LOW_GRAM)
attr(merged_list$FPED$DR1T_Total_Seafood_Sub  , "label") <- "Total Seafood and Substitutes consumed (grams)" 
```

### Code a new variable that summarizes the red and processed meats

```{r}
merged_list$FPED <- merged_list$FPED %>%
  mutate(DR1T_Total_Red_Processed_Meat =  DR1T_PF_MEAT_GRAM+ DR1T_PF_CUREDMEAT_GRAM + DR1T_PF_ORGAN_GRAM )
merged_list$FPED <- merged_list$FPED %>%
  relocate(DR1T_Total_Red_Processed_Meat, .after = DR1T_PF_ORGAN_GRAM)
attr(merged_list$FPED$DR1T_Total_Red_Processed_Meat  , "label") <- "Total red and processed meats consumed (grams)" 
str(merged_list$FPED)
```

### Code a new variable that contains the total grams a person has eaten a day, and include only the variables from the PHDI-US.

```{r}
# Columns to sum up
columns_to_sum <- c("DR1T_F_TOTAL_GRAM", "DR1T_V_DRKGR_GRAM", "DR1T_V_REDOR_TOTAL_GRAM", 
                    "DR1T_V_STARCHY_TOTAL_GRAM", "DR1T_V_OTHER_GRAM", "DR1T_PF_LEGUMES_GRAM", 
                    "DR1T_G_WHOLE_GRAM", "DR1T_PF_MEAT_GRAM", "DR1T_PF_CUREDMEAT_GRAM", 
                    "DR1T_PF_ORGAN_GRAM", "DR1T_PF_POULT_GRAM", "DR1T_PF_SEAFD_HI_GRAM", 
                    "DR1T_PF_SEAFD_LOW_GRAM", "DR1T_PF_EGGS_GRAM", "DR1T_PF_NUTSDS_GRAM", 
                    "DR1T_D_TOTAL_GRAM", "DR1T_OILS", "DR1T_SOLID_FATS", "DR1T_ADD_SUGARS_GRAM")

# Perform the sum
total_per_day <- rowSums(merged_list$FPED[, columns_to_sum], na.rm = TRUE)

# Add the new variable to the tibble
merged_list$FPED <- cbind(merged_list$FPED, DR1T_Total_Grams_Per_Day = total_per_day)
attr(merged_list$FPED$DR1T_Total_Grams_Per_Day  , "label") <- "Total grams consumed per day (grams)" 
str(merged_list$FPED)
summary(merged_list$FPED$DR1T_Total_Grams_Per_Day, na.rm = T)

```

### SODAs

**The sodas are computed as added sugars in the FPEDs**! They can be checked in the food codes table made available online: <https://www.ars.usda.gov/northeast-area/beltsville-md-bhnrc/beltsville-human-nutrition-research-center/food-surveys-research-group/docs/fped-databases/>

<https://fdc.nal.usda.gov/fdc-app.html#/food-details/2346034/nutrients> (website that shows the nutritional values for the food codes).

What is a good definition for sweetened beverages? --\>the one by the WHO: <https://www.ncbi.nlm.nih.gov/books/NBK285538/>

WHO definition: Free sugars include monosaccharides and disaccharides added to foods and beverages by the manufacturer, cook or consumer, and sugars naturally present in **honey, syrups, fruit juices and fruit juice concentrates.** In both adults and children, WHO recommends reducing the intake of free sugars to less than 10% of total energy intake

So then for fruit juices and fruit juice concentrates, the sugars should be added to the "added sugar" variable as well. Which is at least in the FPED 05/06 not the case.

\--\> went through the Food codes list of 2005/2006, checked if free sugars were also scored in the added_sugars variable. Therefore I used the following terms:

-   **Juice**

-   **Honey**

-   **Syrups**

-   **Juice concentrate**

If the ingredients were not scored in the added_sugar variable, the FPED_Ind variable was screened to see if that food code/the ingredient was even in the data set.

In the Excel sheet:

-   green = is not scored as added_sugar and is in the FPED_Ind variable list

-   Red = is not scored as added_sugar, but is not in the FPED_Ind variable list

-   Blue = is already scored as added_sugar

-   yellow = if they then were added into the merged_list\$FPED\$DR1T_ADD_SUGARS_GRAM variable

```{r}

# Check if the food code exists in the variable, and change the food code number every time
if (any(91406500%in% merged_list$FPED_IND$DR1IFDCD)) {
  print(" exists in the variable")
} else {
  print(" does not exist in the variable")
}

```

So if the ingredient/food code was not in the FPED_Ind list, nothing else was done. If it was, then the food code was entered into this [website](https://fdc.nal.usda.gov/fdc-app.html#/food-details/2346034/nutrients) to get the nutritional values, respectively the sugar content. Then the FPED_Ind list was screened for the food code, to get the the grams consumed of the foods/beverages, and then the sugar content was calculated. After that, the Added_sugar variables was changed for the individual / participant.

WOULD IT MAKE SENSE TO DEFINE A CUT OFF VALUE, SO WE DO NOT NEED TO CHANGE ALL THE SUGAR VARIABLES?\
E.G. LIME / LEMON JUICE HAVE LIKE 1 TO 3GRAMS OF SUGAR IN 100ML

#### Updating the sugar content of free sugars into the merged_list\$FPED sugar variable

#####  61201010

```{r}
# Find the rows where the Food code number 61201010 is present in the column 
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 61201010, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (9.1/100)


for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}

print(rows_with_food_code)


glimpse(rows_with_food_code$DR1I_ADD_SUGARS)
glimpse(merged_list$FPED %>% filter(SEQN == 32113))
#for SEQN number = 32113: 
## The sugar added from the grapefruit juice is = 22.49.
### The sugar content before for that person was : 114
#### the sugar content after adding the sugar form the grapefruit juice is: 136.4952 
##### seems to work for the Grapefruit juice!!
##### double checked other SEQN numbers that did not have to food code / did not consume grapefruit juice --> nothing was changed in the sugar variable for that SEQN! 

```

##### 61201020

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 61201020, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (7.42/100)


for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 61201620

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 61201620, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (9.55/100)
print(rows_with_food_code)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}

glimpse(merged_list$FPED %>% filter(SEQN == 35454)) 
```

##### 61210000

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 61210000, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (8.18/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 61210010

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 61210010, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (8.08/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 61210220

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 61210220, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (8.18/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 61210250

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 61210250, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (8.18/100) #same as above

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 61210620

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 61210620, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (8.47/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 61210820

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 61210820, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (8.48/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 61213220

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 61213220, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (9.9/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 61213800

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 61213800, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (8.18/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 64100100

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 64100100, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (10.4/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 64100110

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 64100110, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (10.9/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 64100200

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 64100200, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (9.04/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 64101010

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 64101010, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (9.62/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 64104010

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 64104010, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (10.1/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 64104600

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 64104600, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (7.7/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 64105400

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 64105400, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (3.41/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 64116020

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 64116020, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (14.2/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 64120010

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 64120010, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (13.9/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 64121000

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 64121000, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (13.4/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 64124020

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 64124020, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (9.98/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 64132010

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 64132010, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (16.4/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 64132500

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 64132500, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (7.7/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 64133100

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 64133100, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (6.2/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 75200700

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 75200700, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (3.75/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 91406500

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 91406500, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (42/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 92433000

```{r}
rows_with_food_code <- merged_list$FPED_IND[merged_list$FPED_IND$DR1IFDCD == 92433000, ]
rows_with_food_code$DR1I_ADD_SUGARS <- rows_with_food_code$DR1IGRMS * (6.38/100)

for (i in 1:nrow(rows_with_food_code)) {
  row_index <- which(merged_list$FPED$SEQN == rows_with_food_code$SEQN[i])
  merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] <- 
    merged_list$FPED[row_index, "DR1T_ADD_SUGARS_GRAM"] + rows_with_food_code$DR1I_ADD_SUGARS[i]
}
```

##### 

## Compute the PHDI-US

### Code the basic calculation of the PHDI-US

```{r}

#the following code is probably best put into a function! But here I get error messages because the list I would need is the merged_list$FPED. 

#the maximal and minimum scores you can get in each category
    PHDI_MIN = 0
    PHDI_MAX = 10
    PHDI_MAX_2 = 5 #ratio components

#the upper and lower limit(s) for every variable are percentages of total grams eaten that day of one participant
    PHDI_Nuts_min = 0 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_Nuts_max = 0.025 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_Legumes_min = 0 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_Legumes_max = 0.085 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_Fruits_min = 0 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_Fruits_max = 0.101 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_NS_Veg_min = 0 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_NS_Veg_max = 0.152* merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_W_Grains_min = 0 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_W_Grains_max = 0.25 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_Seaf_S_min1 = 0 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_Seaf_S_min2 = 0.051 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_Seaf_S_max = 0.014 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_ST_Veg_min1 = 0 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_ST_Veg_min2 = 0.051 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_ST_Veg_max = 0.025 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_Dairy_min1 = 0 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_Dairy_min2 = 0.253 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_Dairy_max = 0.126 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_UNS_Oils_min1 = 0* merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_UNS_Oils_min2 = 0.04* merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_UNS_Oils_max = 0.02 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_Eggs_min = 0.013 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_Eggs_max = 0.007 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_RP_Meat_min = 0.014 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_RP_Meat_max = 0.007 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_Poultry_min = 0.29 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_Poultry_max = 0.015 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_Sat_Fats_min = 0.006 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_Sat_Fats_max = 0.003 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_Add_Sugars_min = 0.016 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    PHDI_Add_Sugars_max = 0.008 * merged_list$FPED$DR1T_Total_Grams_Per_Day
    
    
# three functions, one for adequacy components, once for optimum components and once for moderation components
    SCORE_ADEQUACY = function(actual_serv, min_serv, max_serv, min_score, max_score) {
      case_when(
        actual_serv >= max_serv ~ max_score,
        actual_serv == min_serv ~ min_score,
        TRUE ~ min_score + (actual_serv - min_serv) * max_score / (max_serv - min_serv)
      )
    }
    
    SCORE_MODERATION = function(actual_serv, min_serv, max_serv, min_score, max_score) {
      case_when(
        actual_serv >= min_serv ~ min_score,
        actual_serv <= max_serv ~ max_score,
        TRUE ~ min_score + (actual_serv - min_serv) * max_score / (max_serv - min_serv)
      )
    }
#if the actual serving size is between the min_serv1 and the max_serv, then we need another equation than when actual_serv is between max_serv and min_serv2    
  SCORE_OPTIMUM = function(actual_serv, min_serv1, min_serv2, max_serv, min_score, max_score) {
      case_when(
        actual_serv == max_serv ~ max_score,
        actual_serv == min_serv1 ~ min_score,
        actual_serv >= min_serv2 ~ min_score,
        actual_serv < max_serv ~ ((min_score + (actual_serv - min_serv1) * max_score) / (max_serv - min_serv1)),
        TRUE ~  min_score + (actual_serv - min_serv2) * max_score / (max_serv - min_serv2)
      )
    }
    
#  Ratio components?
# Dark green vegetables (grams) / Total red and orange vegetables (tomatoes + other red and orange) (grams) + Other vegetables not in the vegetable components listed above (grams)
#  DR1T_V_DRKGR_GRAM / DR1T_V_REDOR_TOTAL_GRAM  + DR1T_V_OTHER_GRAM 
# and the same is true for the red veggies --> red veggies / all other non starchy veggies
  
  SCORE_RATIO = function(green_veg, red_veg, other_veg, min_score, max_score) {
    ratio = (green_veg / (red_veg + other_veg))*100
    case_when(
      ratio == 33.3 ~ max_score,
      ratio < 33.3 ~ pmax((ratio / 33.3) * max_score, min_score),
      ratio > 33.3 ~ pmax(((100 - ratio) / (100 - 33.3)) * max_score, min_score)
    )
  }

#Adequacy components   
  PHDI_Nuts_and_Peanuts = SCORE_ADEQUACY(merged_list$FPED$DR1T_PF_NUTSDS_GRAM, PHDI_Nuts_min, PHDI_Nuts_max, PHDI_MIN, PHDI_MAX)
  PHDI_Legumes = SCORE_ADEQUACY(merged_list$FPED$DR1T_PF_LEGUMES_GRAM, PHDI_Legumes_min, PHDI_Legumes_max, PHDI_MIN, PHDI_MAX)
  PHDI_Fruits = SCORE_ADEQUACY(merged_list$FPED$DR1T_F_TOTAL_GRAM, PHDI_Fruits_min, PHDI_Fruits_max, PHDI_MIN, PHDI_MAX)
  PHDI_NS_Veggies = SCORE_ADEQUACY(merged_list$FPED$DR1T_Total_Non_starchy_Veggies, PHDI_NS_Veg_min, PHDI_NS_Veg_max, PHDI_MIN, PHDI_MAX)
  PHDI_Whole_Grains = SCORE_ADEQUACY(merged_list$FPED$DR1T_G_WHOLE_GRAM, PHDI_W_Grains_min, PHDI_W_Grains_max, PHDI_MIN, PHDI_MAX)
#Optimum components  
  PHDI_Seafood_Sub = SCORE_OPTIMUM(merged_list$FPED$DR1T_Total_Seafood_Sub, PHDI_Seaf_S_min1, PHDI_Seaf_S_min2, PHDI_Seaf_S_max, PHDI_MIN, PHDI_MAX)
  PHDI_Starchy_Veggies = SCORE_OPTIMUM(merged_list$FPED$DR1T_V_STARCHY_TOTAL_GRAM, PHDI_ST_Veg_min1, PHDI_ST_Veg_min2, PHDI_ST_Veg_max, PHDI_MIN, PHDI_MAX)
  PHDI_Dairy = SCORE_OPTIMUM(merged_list$FPED$DR1T_D_TOTAL_GRAM, PHDI_Dairy_min1, PHDI_Dairy_min2, PHDI_Dairy_max, PHDI_MIN, PHDI_MAX)
  PHDI_Unsaturated_Oils = SCORE_OPTIMUM(merged_list$FPED$DR1T_OILS, PHDI_UNS_Oils_min1, PHDI_UNS_Oils_min2, PHDI_UNS_Oils_max, PHDI_MIN, PHDI_MAX)
#Ratio components
  PHDI_DGV_Ratio = SCORE_RATIO(merged_list$FPED$DR1T_V_DRKGR_GRAM, merged_list$FPED$DR1T_V_REDOR_TOTAL_GRAM, merged_list$FPED$DR1T_V_OTHER_GRAM, PHDI_MIN, PHDI_MAX_2)
  PHDI_ReV_Ratio = SCORE_RATIO(merged_list$FPED$DR1T_V_REDOR_TOTAL_GRAM, merged_list$FPED$DR1T_V_DRKGR_GRAM, merged_list$FPED$DR1T_V_OTHER_GRAM, PHDI_MIN, PHDI_MAX_2)
#Moderation compnents
  PHDI_Eggs = SCORE_MODERATION(merged_list$FPED$DR1T_PF_EGGS_GRAM, PHDI_Eggs_min, PHDI_Eggs_max, PHDI_MIN, PHDI_MAX)
  PHDI_Red_Proc_Meat = SCORE_MODERATION(merged_list$FPED$DR1T_Total_Red_Processed_Meat, PHDI_RP_Meat_min, PHDI_RP_Meat_max, PHDI_MIN, PHDI_MAX)
  PHDI_Poultry = SCORE_MODERATION(merged_list$FPED$DR1T_PF_POULT_GRAM, PHDI_Poultry_min, PHDI_Poultry_max, PHDI_MIN, PHDI_MAX)
  PHDI_Saturated_Fats = SCORE_MODERATION(merged_list$FPED$DR1T_SOLID_FATS, PHDI_Sat_Fats_min, PHDI_Sat_Fats_max, PHDI_MIN, PHDI_MAX)
  PHDI_Added_Sugars = SCORE_MODERATION(merged_list$FPED$DR1T_ADD_SUGARS_GRAM, PHDI_Add_Sugars_min, PHDI_Add_Sugars_max, PHDI_MIN, PHDI_MAX)

# the PHDI for every individual for day 1
PHDI_all_D1 = PHDI_Nuts_and_Peanuts + PHDI_Legumes + PHDI_Fruits + PHDI_NS_Veggies+PHDI_Whole_Grains+PHDI_Seafood_Sub+PHDI_Starchy_Veggies+PHDI_Dairy+PHDI_Unsaturated_Oils+PHDI_DGV_Ratio+PHDI_ReV_Ratio+PHDI_Eggs+PHDI_Red_Proc_Meat+PHDI_Poultry+PHDI_Saturated_Fats+PHDI_Added_Sugars
  
  
hist(PHDI_all_D1)
summary(PHDI_all_D1)
summary(PHDI_Added_Sugars)
hist(PHDI_Added_Sugars)
```

### Add code, so if foods within the Legumes or/and Peanuts exceed the optimum level, the "rest" can be added to the Seafood and Substitute variable

```{r}

###### Nuts
excess_N <- ifelse(merged_list$FPED$DR1T_PF_NUTSDS_GRAM > PHDI_Nuts_max & 
                 merged_list$FPED$DR1T_Total_Seafood_Sub < PHDI_Seaf_S_max,
                 merged_list$FPED$DR1T_PF_NUTSDS_GRAM - PHDI_Nuts_max, 0)

merged_list$FPED$DR1T_Total_Seafood_Sub_new <- ifelse(excess_N + merged_list$FPED$DR1T_Total_Seafood_Sub >= PHDI_Seaf_S_max, PHDI_Seaf_S_max, excess_N + merged_list$FPED$DR1T_Total_Seafood_Sub)


PHDI_Seafood_Sub_new = SCORE_OPTIMUM(merged_list$FPED$DR1T_Total_Seafood_Sub_new, PHDI_Seaf_S_min1, PHDI_Seaf_S_min2, PHDI_Seaf_S_max, PHDI_MIN, PHDI_MAX)
summary(PHDI_Seafood_Sub_new)


###### Legumes

excess_L <- ifelse(merged_list$FPED$DR1T_V_LEGUMES_GRAM > PHDI_Legumes_max & 
                 merged_list$FPED$DR1T_Total_Seafood_Sub < PHDI_Seaf_S_max,
                 merged_list$FPED$DR1T_V_LEGUMES_GRAM - PHDI_Legumes_max, 0)

merged_list$FPED$DR1T_Total_Seafood_Sub_new <- ifelse(excess_L+ merged_list$FPED$DR1T_Total_Seafood_Sub >= PHDI_Seaf_S_max, PHDI_Seaf_S_max, excess_L+ merged_list$FPED$DR1T_Total_Seafood_Sub)


PHDI_Seafood_Sub_new = SCORE_OPTIMUM(merged_list$FPED$DR1T_Total_Seafood_Sub_new, PHDI_Seaf_S_min1, PHDI_Seaf_S_min2, PHDI_Seaf_S_max, PHDI_MIN, PHDI_MAX)


PHDI_all_D1_Excess = PHDI_Nuts_and_Peanuts + PHDI_Legumes + PHDI_Fruits + PHDI_NS_Veggies+PHDI_Whole_Grains+PHDI_Seafood_Sub_new+PHDI_Starchy_Veggies+PHDI_Dairy+PHDI_Unsaturated_Oils+PHDI_DGV_Ratio+PHDI_ReV_Ratio+PHDI_Eggs+PHDI_Red_Proc_Meat+PHDI_Poultry+PHDI_Saturated_Fats+PHDI_Added_Sugars

```

#### Difference between PHDI normal and if compensated?

```{r}
summary(PHDI_all_D1)
summary(PHDI_all_D1_Excess)
summary(PHDI_Added_Sugars)
hist(PHDI_Added_Sugars)
hist(PHDI_all_D1)
hist(PHDI_all_D1_Excess)
```

### Trying to see if the PHDI code is correct on a smaller sample

```{r}
# Extract the first 5 rows from each data frame within merged_list$FPED
subsetted_list <- merged_list$FPED[1:5, ]

# Print the resulting list of data frames
print(subsetted_list)

#add the PHDI min and max
PHDI_MIN = 0
    PHDI_MAX = 10
    PHDI_MAX_2 = 5 #ratio components

PHDI_Nuts_min = 0 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_Nuts_max = 0.025 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_Legumes_min = 0 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_Legumes_max = 0.085 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_Fruits_min = 0 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_Fruits_max = 0.101 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_NS_Veg_min = 0 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_NS_Veg_max = 0.152* subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_W_Grains_min = 0 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_W_Grains_max = 0.25 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_Seaf_S_min1 = 0 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_Seaf_S_min2 = 0.051 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_Seaf_S_max = 0.014 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_ST_Veg_min1 = 0 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_ST_Veg_min2 = 0.051 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_ST_Veg_max = 0.025 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_Dairy_min1 = 0 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_Dairy_min2 = 0.253 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_Dairy_max = 0.126 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_UNS_Oils_min1 = 0* subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_UNS_Oils_min2 = 0.04* subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_UNS_Oils_max = 0.02 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_Eggs_min = 0.013 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_Eggs_max = 0.007 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_RP_Meat_min = 0.014 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_RP_Meat_max = 0.007 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_Poultry_min = 0.29 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_Poultry_max = 0.015 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_Sat_Fats_min = 0.006 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_Sat_Fats_max = 0.003 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_Add_Sugars_min = 0.016 * subsetted_list$DR1T_Total_Grams_Per_Day
    PHDI_Add_Sugars_max = 0.008 * subsetted_list$DR1T_Total_Grams_Per_Day    


#Insert the PHDI code and change merged_list for subsetted_list
  PHDI_SUBSETTED_Nuts_and_Peanuts = SCORE_ADEQUACY(subsetted_list$DR1T_PF_NUTSDS_GRAM, PHDI_Nuts_min, PHDI_Nuts_max, PHDI_MIN, PHDI_MAX)
  PHDI_SUBSETTED_Legumes = SCORE_ADEQUACY(subsetted_list$DR1T_PF_LEGUMES_GRAM, PHDI_Legumes_min, PHDI_Legumes_max, PHDI_MIN, PHDI_MAX)
  PHDI_SUBSETTED_Fruits = SCORE_ADEQUACY(subsetted_list$DR1T_F_TOTAL_GRAM, PHDI_Fruits_min, PHDI_Fruits_max, PHDI_MIN, PHDI_MAX)
  PHDI_SUBSETTED_NS_Veggies = SCORE_ADEQUACY(subsetted_list$DR1T_Total_Non_starchy_Veggies, PHDI_NS_Veg_min, PHDI_NS_Veg_max, PHDI_MIN, PHDI_MAX)
  PHDI_SUBSETTED_Whole_Grains = SCORE_ADEQUACY(subsetted_list$DR1T_G_WHOLE_GRAM, PHDI_W_Grains_min, PHDI_W_Grains_max, PHDI_MIN, PHDI_MAX)
#Optimum components  
  PHDI_SUBSETTED_Seafood_Sub = SCORE_OPTIMUM(subsetted_list$DR1T_Total_Seafood_Sub, PHDI_Seaf_S_min1, PHDI_Seaf_S_min2, PHDI_Seaf_S_max, PHDI_MIN, PHDI_MAX)
  PHDI_SUBSETTED_Starchy_Veggies = SCORE_OPTIMUM(subsetted_list$DR1T_V_STARCHY_TOTAL_GRAM, PHDI_ST_Veg_min1, PHDI_ST_Veg_min2, PHDI_ST_Veg_max, PHDI_MIN, PHDI_MAX)
  PHDI_SUBSETTED_Dairy = SCORE_OPTIMUM(subsetted_list$DR1T_D_TOTAL_GRAM, PHDI_Dairy_min1, PHDI_Dairy_min2, PHDI_Dairy_max, PHDI_MIN, PHDI_MAX)
  PHDI_SUBSETTED_Unsaturated_Oils = SCORE_OPTIMUM(subsetted_list$DR1T_OILS, PHDI_UNS_Oils_min1, PHDI_UNS_Oils_min2, PHDI_UNS_Oils_max, PHDI_MIN, PHDI_MAX)
#Ratio components
  PHDI_SUBSETTED_DGV_Ratio = SCORE_RATIO(subsetted_list$DR1T_V_DRKGR_GRAM, subsetted_list$DR1T_V_REDOR_TOTAL_GRAM, subsetted_list$DR1T_V_OTHER_GRAM, PHDI_MIN, PHDI_MAX_2)
  PHDI_SUBSETTED_ReV_Ratio = SCORE_RATIO(subsetted_list$DR1T_V_REDOR_TOTAL_GRAM, subsetted_list$DR1T_V_DRKGR_GRAM, subsetted_list$DR1T_V_OTHER_GRAM, PHDI_MIN, PHDI_MAX_2)
#Moderation compnents
  PHDI_SUBSETTED_Eggs = SCORE_MODERATION(subsetted_list$DR1T_PF_EGGS_GRAM, PHDI_Eggs_min, PHDI_Eggs_max, PHDI_MIN, PHDI_MAX)
  PHDI_SUBSETTED_Red_Proc_Meat = SCORE_MODERATION(subsetted_list$DR1T_Total_Red_Processed_Meat, PHDI_RP_Meat_min, PHDI_RP_Meat_max, PHDI_MIN, PHDI_MAX)
  PHDI_SUBSETTED_Poultry = SCORE_MODERATION(subsetted_list$DR1T_PF_POULT_GRAM, PHDI_Poultry_min, PHDI_Poultry_max, PHDI_MIN, PHDI_MAX)
  PHDI_SUBSETTED_Saturated_Fats = SCORE_MODERATION(subsetted_list$DR1T_SOLID_FATS, PHDI_Sat_Fats_min, PHDI_Sat_Fats_max, PHDI_MIN, PHDI_MAX)
  PHDI_SUBSETTED_Added_Sugars = SCORE_MODERATION(subsetted_list$DR1T_ADD_SUGARS_GRAM, PHDI_Add_Sugars_min, PHDI_Add_Sugars_max, PHDI_MIN, PHDI_MAX)


excess_N_SUB <- ifelse(subsetted_list$DR1T_PF_NUTSDS_GRAM > PHDI_Nuts_max & 
                 subsetted_list$DR1T_Total_Seafood_Sub < PHDI_Seaf_S_max,
                 subsetted_list$DR1T_PF_NUTSDS_GRAM - PHDI_Nuts_max, 0)

subsetted_list$DR1T_Total_Seafood_Sub_new <- ifelse(excess_N_SUB +subsetted_list$DR1T_Total_Seafood_Sub >=PHDI_Seaf_S_max, PHDI_Seaf_S_max, excess_N_SUB +subsetted_list$DR1T_Total_Seafood_Sub)

PHDI_Seafood_Sub_new = SCORE_OPTIMUM(subsetted_list$DR1T_Total_Seafood_Sub_new, PHDI_Seaf_S_min1, PHDI_Seaf_S_min2, PHDI_Seaf_S_max, PHDI_MIN, PHDI_MAX)
summary(PHDI_Seafood_Sub_new)


###### Legumes

excess_L <- ifelse(subsetted_list$DR1T_V_LEGUMES_GRAM > PHDI_Legumes_max & 
                 subsetted_list$DR1T_Total_Seafood_Sub < PHDI_Seaf_S_max,
                 subsetted_list$DR1T_V_LEGUMES_GRAM - PHDI_Legumes_max, 0)

subsetted_list$DR1T_Total_Seafood_Sub_new <- ifelse(excess_L+subsetted_list$DR1T_Total_Seafood_Sub >=
                                                        PHDI_Seaf_S_max, PHDI_Seaf_S_max,
                                                      excess_L + subsetted_list$DR1T_Total_Seafood_Sub)

PHDI_Seafood_Sub = SCORE_OPTIMUM(subsetted_list$DR1T_Total_Seafood_Sub, PHDI_Seaf_S_min1, PHDI_Seaf_S_min2, PHDI_Seaf_S_max, PHDI_MIN, PHDI_MAX)
summary(PHDI_Seafood_Sub)

PHDI_Subsetted_Seafood_Sub_new = SCORE_OPTIMUM(subsetted_list$DR1T_Total_Seafood_Sub_new, PHDI_Seaf_S_min1, PHDI_Seaf_S_min2, PHDI_Seaf_S_max, PHDI_MIN, PHDI_MAX)
summary(PHDI_Seafood_Sub_new)  
    

# the PHDI for every individual for day 1
PHDI_SUBSETTED_all_D1 = PHDI_SUBSETTED_Nuts_and_Peanuts + PHDI_SUBSETTED_Legumes + PHDI_SUBSETTED_Fruits + PHDI_SUBSETTED_NS_Veggies+PHDI_SUBSETTED_Whole_Grains+PHDI_Subsetted_Seafood_Sub_new+PHDI_SUBSETTED_Starchy_Veggies+PHDI_SUBSETTED_Dairy+PHDI_SUBSETTED_Unsaturated_Oils+PHDI_SUBSETTED_DGV_Ratio+PHDI_SUBSETTED_ReV_Ratio+PHDI_SUBSETTED_Eggs+PHDI_SUBSETTED_Red_Proc_Meat+PHDI_SUBSETTED_Poultry+PHDI_SUBSETTED_Saturated_Fats+PHDI_SUBSETTED_Added_Sugars

summary(PHDI_SUBSETTED_all_D1)

PHDI_SUBSETTED_all_D1
##seems to work!!

```

## Basic descriptions of PHDI

```{r}
library(pastecs)
library(e1071)
summary(PHDI_all_D1_Excess)
hist(PHDI_all_D1_Excess)
round(stat.desc(PHDI_all_D1_Excess, norm=F), 2)
skewness(PHDI_all_D1_Excess, na.rm = T)
qqnorm(PHDI_all_D1_Excess)
qqline(PHDI_all_D1_Excess, col="blue")
ggpairs(PHDI_all_D1_Excess)



model_chol <- lm(PHDI_all_D1_Excess ~ merged_list$LAB_Cholesterol$LBDTCSI)
length(PHDI_all_D1_Excess)
length(merged_list$LAB_Cholesterol$LBDTCSI)
```
