---
title: "PHDI-US_V2"
author: "Laura Schirlo"
date: "2024-03-27"
output: html_document
---

# PHDI-US VERSION 2

## Installing the packages needed

```{r}
install.packages("foreign")
library(foreign)
library(ggplot2); theme_set(theme_bw())
library(pastecs)
library(leaflet)
library(ggpubr)
library(ggfortify)
library(GGally)
library(car)
library(effects)
library(emmeans)
library(MuMIn)
install.packages("devtools") #If you don't have "devtools" installed already
devtools::install_github("jamesjiadazhan/dietaryindex") # Install the package from GitHub
library(dplyr)
library(haven)
library(readr)
library(dietaryindex)

setwd("~/Desktop/Master_thesis")
```

## What is different in the PHDI-US compared to PHDI

-   max score is 150 in PHDI-US and not 140

-   the scores are percentages of total grams consumed, and not total calories consumed

-   eggs= moderation component (0g=10points) in PHDI-US and not a optimum component

-   vegetables are divided in non-starchy veggies & tubers and starchy veggies (in original it is only veggies & tubers and potatoes)

-   fish and seafood is extended to seafood and substitutes

-   vegetable oils are unsaturated oils in the PHDI-US

-   red meat is extended to red and processed meat in PHDI-US

-   Chicken and substitutes is Poultry in the PHDI-US

-   animal fats are saturated fats in the PHDI-US

@param SERV_DATA The raw data file that includes all the serving sizes of foods and nutrients consumed per 1 day\
@param RESPONDENTID The unique participant ID for each participant\
@param GENDER The gender of the participant. 2 is female and 1 is male.\
@param TOTALKCAL_PHDI The total kcal\
@param WGRAIN_SERV_PHDI The serving size of whole grains, unit=grams/day\
@param STARCHY_VEG_SERV_PHDI The serving size of starchy vegetables, such as potatos, cassava, unit=grams/day\
@param VEG_SERV_PHDI The serving size of All vegetable except potatoes, starchy vegetables, and LEGUMES, unit=grams/day\
@param FRT_SERV_PHDI The serving size of All whole fruits and no fruit juice, unit=grams/day\
@param DAIRY_SERV_PHDI The serving size of All dairy products, unit=grams/day\
@param REDPROC_MEAT_SERV_PHDI The serving size of red and processed meats, including Beef, pork, lamb, goat, veal, sausages, bacon, salami, ham, hot dog, deli meat, unit=grams/day\
@param POULTRY_SERV_PHDI The serving size of Poultry, including Chicken, turkey, duck, goose, ostrich, unit=grams/day\
@param EGG_SERV_PHDI The serving size of Eggs with shell, unit=grams/day\
@param FISH_SERV_PHDI The serving size of Fish and shellfish, unit=grams/day\
@param NUTS_SERV_PHDI The serving size of nuts and seeds, including peanuts, tree nuts- - walnuts, almond, hazelnuts, pecan, cashew, pistachio, unit=grams/day\
@param LEGUMES_SERV_PHDI The serving size of Nonsoy LEGUMES, including Beans, peas, lentils, chickpeas, unit=grams/day\
@param SOY_SERV_PHDI The serving size of Soy products, including Tofu, tempeh, soy milk, soy yogurt, soy cheese, unit=grams/day\
@param ADDED_FAT_UNSAT_SERV_PHDI The serving size of Added unsaturated fat, e.g. olive soybean, rapeseed, sunflower, peanuts oil, excluding transfat, unit=grams/day\
@param ADDED_FAT_SAT_TRANS_SERV_PHDI The serving size of Added saturated fats and trans fat, e.g. butter, lard, coconuts oil, palm oil, unit=grams/day\
@param ADDED_SUGAR_SERV_PHDI The serving size of Added sugar, including the added sugar from all sweeteners and fruit juice, unit=grams/day\
@return The PHDI index/score, PHDI and its component scores\

```{r}
# Score calculation for PHDI
PHDI_V2 = function(SERV_DATA, RESPONDENTID, GENDER, TOTALKCAL_PHDI, WGRAIN_SERV_PHDI, STARCHY_VEG_SERV_PHDI, VEG_SERV_PHDI, FRT_SERV_PHDI,DAIRY_SERV_PHDI, REDPROC_MEAT_SERV_PHDI, POULTRY_SERV_PHDI, EGG_SERV_PHDI, FISH_SERV_PHDI, NUTS_SERV_PHDI, LEGUMES_SERV_PHDI, SOY_SERV_PHDI, ADDED_FAT_UNSAT_SERV_PHDI, ADDED_FAT_SAT_TRANS_SERV_PHDI, ADDED_SUGAR_SERV_PHDI) {
    ## Create variables and functions needed for PHDI calculation
    PHDI_MIN = 0
    PHDI_MAX = 10
    PHDI_MAX_2 = 5
    PHDI_MIN_WGRAIN_F_SERV = 0
    PHDI_MAX_WGRAIN_F_SERV = 75
    PHDI_MIN_WGRAIN_M_SERV = 0
    PHDI_MAX_WGRAIN_M_SERV = 90
    PHDI_MIN_STARCHY_VEG_SERV = 200
    PHDI_MAX_STARCHY_VEG_SERV = 50
    PHDI_MIN_VEG_SERV = 0
    PHDI_MAX_VEG_SERV = 300
    PHDI_MIN_FRT_SERV = 0
    PHDI_MAX_FRT_SERV = 200
    PHDI_MIN_DAIRY_SERV = 1000
    PHDI_MAX_DAIRY_SERV = 250
    PHDI_MIN_REDPROC_MEAT_SERV = 100
    PHDI_MAX_REDPROC_MEAT_SERV = 14
    PHDI_MIN_POULTRY_SERV = 100
    PHDI_MAX_POULTRY_SERV = 29
    PHDI_MIN_EGG_SERV = 120
    PHDI_MAX_EGG_SERV = 13
    PHDI_MIN_FISH_SERV = 0
    PHDI_MAX_FISH_SERV = 28
    PHDI_MIN_NUTS_SERV = 0
    PHDI_MAX_NUTS_SERV = 50
    PHDI_MIN_LEGUMES_SERV = 0
    PHDI_MAX_LEGUMES_SERV = 100
    PHDI_MIN_SOY_SERV = 0
    PHDI_MAX_SOY_SERV = 50
    PHDI_MIN_ADDED_FAT_UNSAT_SERV = 3.5
    PHDI_MAX_ADDED_FAT_UNSAT_SERV = 21
    PHDI_MIN_ADDED_FAT_SAT_TRANS_SERV = 10
    PHDI_MAX_ADDED_FAT_SAT_TRANS_SERV = 0
    PHDI_MIN_ADDED_SUGAR_SERV = 25
    PHDI_MAX_ADDED_SUGAR_SERV = 5


    SCORE_HEALTHY = function(actual_serv, min_serv, max_serv, min_score, max_score) {
        case_when(
            actual_serv >= max_serv ~ max_score,
            actual_serv <= min_serv ~ min_score,
            TRUE ~ min_score + (actual_serv - min_serv) * max_score / (max_serv - min_serv)
        )
    }


    SCORE_UNHEALTHY = function(actual_serv, min_serv, max_serv, min_score, max_score) {
        case_when(
            actual_serv >= min_serv ~ min_score,
            actual_serv <= max_serv ~ max_score,
            TRUE ~ min_score + (actual_serv - min_serv) * max_score / (max_serv - min_serv)
        )
    }

    ## update the serving size of ADDED_FAT_UNSAT_SERV_PHDI, ADDED_FAT_SAT_TRANS_SERV_PHDI, and ADDED_SUGAR_SERV_PHDI to % kcal
    SERV_DATA = SERV_DATA %>%
        mutate(
            ### 1 gram of fat = 9 kcal. 1 gram of carbohydrate = 4 kcal. Multiply by 100 to get percentage
            ADDED_FAT_UNSAT_SERV_PHDI = (ADDED_FAT_UNSAT_SERV_PHDI * 9 / TOTALKCAL_PHDI) * 100,
            ADDED_FAT_SAT_TRANS_SERV_PHDI = (ADDED_FAT_SAT_TRANS_SERV_PHDI * 9 / TOTALKCAL_PHDI) * 100,
            ADDED_SUGAR_SERV_PHDI = (ADDED_SUGAR_SERV_PHDI * 4 / TOTALKCAL_PHDI) * 100
        )

    ## PHDI calculation
    SERV_DATA %>%
        dplyr::mutate(
            RESPONDENTID = RESPONDENTID,
            GENDER = GENDER,
            TOTALKCAL_PHDI = TOTALKCAL_PHDI,
            PHDI_WGRAIN = case_when(
                # GENDER = 2 is female
                GENDER == 2 & WGRAIN_SERV_PHDI >= PHDI_MAX_WGRAIN_F_SERV ~ PHDI_MAX,
                GENDER == 2 & WGRAIN_SERV_PHDI <= PHDI_MIN_WGRAIN_F_SERV ~ PHDI_MIN,
                GENDER == 2 & WGRAIN_SERV_PHDI > PHDI_MIN_WGRAIN_F_SERV & WGRAIN_SERV_PHDI < PHDI_MAX_WGRAIN_F_SERV ~ PHDI_MIN + (WGRAIN_SERV_PHDI - PHDI_MIN_WGRAIN_F_SERV) * PHDI_MAX / (PHDI_MAX_WGRAIN_F_SERV - PHDI_MIN_WGRAIN_F_SERV),
                GENDER == 1 & WGRAIN_SERV_PHDI >= PHDI_MAX_WGRAIN_M_SERV ~ PHDI_MAX,
                GENDER == 1 & WGRAIN_SERV_PHDI <= PHDI_MIN_WGRAIN_M_SERV ~ PHDI_MIN,
                GENDER == 1 & WGRAIN_SERV_PHDI > PHDI_MIN_WGRAIN_M_SERV & WGRAIN_SERV_PHDI < PHDI_MAX_WGRAIN_M_SERV ~ PHDI_MIN + (WGRAIN_SERV_PHDI - PHDI_MIN_WGRAIN_M_SERV) * PHDI_MAX / (PHDI_MAX_WGRAIN_M_SERV - PHDI_MIN_WGRAIN_M_SERV),
            ),
            PHDI_STARCHY_VEG = SCORE_UNHEALTHY(STARCHY_VEG_SERV_PHDI, PHDI_MIN_STARCHY_VEG_SERV, PHDI_MAX_STARCHY_VEG_SERV, PHDI_MIN, PHDI_MAX),
            PHDI_VEG = SCORE_HEALTHY(VEG_SERV_PHDI, PHDI_MIN_VEG_SERV, PHDI_MAX_VEG_SERV, PHDI_MIN, PHDI_MAX),
            PHDI_FRT = SCORE_HEALTHY(FRT_SERV_PHDI, PHDI_MIN_FRT_SERV, PHDI_MAX_FRT_SERV, PHDI_MIN, PHDI_MAX),
            PHDI_DAIRY = SCORE_UNHEALTHY(DAIRY_SERV_PHDI, PHDI_MIN_DAIRY_SERV, PHDI_MAX_DAIRY_SERV, PHDI_MIN, PHDI_MAX),
            PHDI_REDPROC_MEAT = SCORE_UNHEALTHY(REDPROC_MEAT_SERV_PHDI, PHDI_MIN_REDPROC_MEAT_SERV, PHDI_MAX_REDPROC_MEAT_SERV, PHDI_MIN, PHDI_MAX),
            PHDI_POULTRY = SCORE_UNHEALTHY(POULTRY_SERV_PHDI, PHDI_MIN_POULTRY_SERV, PHDI_MAX_POULTRY_SERV, PHDI_MIN, PHDI_MAX),
            PHDI_EGG = SCORE_UNHEALTHY(EGG_SERV_PHDI, PHDI_MIN_EGG_SERV, PHDI_MAX_EGG_SERV, PHDI_MIN, PHDI_MAX),
            PHDI_FISH = SCORE_HEALTHY(FISH_SERV_PHDI, PHDI_MIN_FISH_SERV, PHDI_MAX_FISH_SERV, PHDI_MIN, PHDI_MAX),
            PHDI_NUTS = SCORE_HEALTHY(NUTS_SERV_PHDI, PHDI_MIN_NUTS_SERV, PHDI_MAX_NUTS_SERV, PHDI_MIN, PHDI_MAX),
            PHDI_LEGUMES = SCORE_HEALTHY(LEGUMES_SERV_PHDI, PHDI_MIN_LEGUMES_SERV, PHDI_MAX_LEGUMES_SERV, PHDI_MIN, PHDI_MAX_2),
            PHDI_SOY = SCORE_HEALTHY(SOY_SERV_PHDI, PHDI_MIN_SOY_SERV, PHDI_MAX_SOY_SERV, PHDI_MIN, PHDI_MAX_2),
            PHDI_ADDED_FAT_UNSAT = SCORE_HEALTHY(ADDED_FAT_UNSAT_SERV_PHDI, PHDI_MIN_ADDED_FAT_UNSAT_SERV, PHDI_MAX_ADDED_FAT_UNSAT_SERV, PHDI_MIN, PHDI_MAX),
            PHDI_ADDED_FAT_SAT = SCORE_UNHEALTHY(ADDED_FAT_SAT_TRANS_SERV_PHDI, PHDI_MIN_ADDED_FAT_SAT_TRANS_SERV, PHDI_MAX_ADDED_FAT_SAT_TRANS_SERV, PHDI_MIN, PHDI_MAX),
            PHDI_ADDED_SUGAR = SCORE_UNHEALTHY(ADDED_SUGAR_SERV_PHDI, PHDI_MIN_ADDED_SUGAR_SERV, PHDI_MAX_ADDED_SUGAR_SERV, PHDI_MIN, PHDI_MAX),
            PHDI_ALL = PHDI_WGRAIN + PHDI_STARCHY_VEG + PHDI_VEG + PHDI_FRT + PHDI_DAIRY + PHDI_REDPROC_MEAT + PHDI_POULTRY + PHDI_EGG + PHDI_FISH + PHDI_NUTS + PHDI_LEGUMES + PHDI_SOY + PHDI_ADDED_FAT_UNSAT + PHDI_ADDED_FAT_SAT + PHDI_ADDED_SUGAR
        ) %>%
        dplyr::select(RESPONDENTID, GENDER, PHDI_ALL, TOTALKCAL_PHDI, PHDI_WGRAIN, PHDI_STARCHY_VEG, PHDI_VEG, PHDI_FRT, PHDI_DAIRY, PHDI_REDPROC_MEAT, 
                      PHDI_POULTRY, PHDI_EGG, PHDI_FISH, PHDI_NUTS, PHDI_LEGUMES, PHDI_SOY, PHDI_ADDED_FAT_UNSAT, PHDI_ADDED_FAT_SAT, PHDI_ADDED_SUGAR)
}

```

```{r}
save.image(file = "workspace_backup.RData")

load("~/Desktop/Master_thesis/NHANES_combined_GitHub/NHANES_20072008.rda")
```
